Community-Centric Innovation

### 2014-02-20 paper.tex
commons

@@

Networked cryptocurrency communities level the playground for all participants.

As the source code for creating a

>>>>

A core principle of community networks is precisely the sharing of the network as a commons good.
There is no single owner of the network.
In fact there is no owner of the network.
Even though the participants may own the pieces of hardware that they contributed to the network, the network as a whole belongs the community.
As the value of the network increases with the number of participants, the community have an incentive to freely share network resources to invite others to join the network.

@@

There are also properties of networked cryptocurrencies related to their cryptographical nature.
These currencies do not require the users to trust a third party.
The trust relies on cryptographic primitives that have proven to be robust over the years.
The reliance on secret keys makes it possible to save the same money in more than one place at the same time.
Even if one of the copies of the secret keys is lost, the owner can still access the money if she has access to a second copy.
More sophisticated techniques can be used to achieve greater degrees of security. 
For example, the secret can be divided in three parts in such a way that two out of the three parts are needed to access the money.
Secrets can also be kept in the brain, with no physical proof of the ownership of the money.

As cryptocurrencies are based on free libre software, anyone can create a new currency.
If a currency is used by a single individual is not very useful.
The potential of networked cryptocurrencies evidences when they are used by communities.
The communities can create or agree in a currency for their internal exchanges.
As a result, the currency is impregnated by the values and ethical standards of the community.

The people can choose which currency to use and which community to join.
In this choice, there is an implicit commitment to support certain values and principles.
By joining a particular community and currency, the user strengthens that particular community by offering productive force and services.
The currency is a commons resource used by the whole community.
The value of currency increases as the number of users and transactions increases.
Therefore, the members of a community have an incentive to devote some currency resources to attract new members to the community.
